Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2021-08-26 docs/00-manuscripts/mdpi/manuscript.tex
capital D

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{Conceptualization, Patrick Schratz and Alexander Brenning; methodology, Patrick Schratz, José Cortés and Jannes Muenchow and Bernd Bischl; software, Patrick Schratz; validation, Patrick Schratz and Alexander Brenning; formal analysis, Patrick Schratz, Alexander Brenning, José Cortés and Bernd Bischl; investigation, Patrick Schratz; resources, Eugenia Iturritxa and Patrick Schratz; data curation, Patrick Schratz and Eugenia Iturritxa; writing---original draft preparation, Patrick Schratz; writing---review and editing, Patrick Schratz and Alexander Brenning; visualization, Patrick Schratz; supervision, Alexander Brenning and Bernd Bischl; project administration, Alexander Brenning; funding acquisition, Alexander Brenning. All authors have read and agreed to the published version of the manuscript.}

@@

The image acquisitions were originally attempted during one day (29.10.2016).
due to the variable meteorological conditions some stands had to be imaged one day later.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{Conceptualization, Patrick Schratz and Alexander Brenning; methodology, Patrick Schratz, José Cortés, Jannes Muenchow and Bernd Bischl; software, Patrick Schratz; validation, Patrick Schratz and Alexander Brenning; formal analysis, Patrick Schratz, Alexander Brenning, José Cortés and Bernd Bischl; investigation, Patrick Schratz; resources, Eugenia Iturritxa and Patrick Schratz; data curation, Patrick Schratz and Eugenia Iturritxa; writing---original draft preparation, Patrick Schratz; writing---review and editing, Patrick Schratz and Alexander Brenning; visualization, Patrick Schratz; supervision, Alexander Brenning and Bernd Bischl; project administration, Alexander Brenning; funding acquisition, Alexander Brenning. All authors have read and agreed to the published version of the manuscript.}

@@

The image acquisitions were originally attempted during one day (29.10.2016).
Due to the variable meteorological conditions some stands had to be imaged one day later.
